%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\translate{\cvsection{Resumen}}{\cvsection{Summary}}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}
  \translate{
    Como físico y desarrollador de software \emph{full-stack}, aporto una combinación única de experiencia científica y habilidades técnicas al campo del desarrollo de software. Con una sólida formación en aplicaciones web, de escritorio y científicas, he adquirido una valiosa experiencia en el desarrollo de soluciones de software y la creación de infraestructuras sólidas. Mi pasión por estar al día con las últimas tecnologías me impulsa a aprender y explorar continuamente los avances de vanguardia. Me dedico a entregar resultados de alta calidad y a prosperar en entornos dinámicos e innovadores.
  }{
    As a physicist and full-stack software developer, I bring a unique blend of scientific expertise and technical skills to the field of software development. With a strong background in web, desktop, and scientific applications, I have gained valuable experience in developing software solutions and building robust infrastructures. My passion for staying up-to-date with the latest technologies drives me to continuously learn and explore cutting-edge advancements. I am dedicated to delivering high-quality results and thrive in dynamic and innovative environments.
  }
\end{cvparagraph}
